%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Stylish Article
% LaTeX Template
% Version 2.0 (13/4/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Mathias Legrand (legrand.mathias@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{SelfArx} % Document font size and equations flushed left

\usepackage{lettrine}
\usepackage{graphicx}
\usepackage{lipsum}

\setlength\parindent{0pt}

%----------------------------------------------------------------------------------------
%	COLUMNS
%----------------------------------------------------------------------------------------

\setlength{\columnsep}{0.55cm} % Distance between the two columns of text
\setlength{\fboxrule}{0.75pt} % Width of the border around the abstract

%----------------------------------------------------------------------------------------
%	COLORS
%----------------------------------------------------------------------------------------

\definecolor{color1}{RGB}{0,0,90} % Color of the article title and sections
\definecolor{color2}{RGB}{0,20,20} % Color of the boxes behind the abstract and headings

%----------------------------------------------------------------------------------------
%	HYPERLINKS
%----------------------------------------------------------------------------------------

\usepackage{hyperref} % Required for hyperlinks
\hypersetup{hidelinks,colorlinks,breaklinks=true,urlcolor=color2,citecolor=color1,linkcolor=color1,bookmarksopen=false,pdftitle={Title},pdfauthor={Author}}

%----------------------------------------------------------------------------------------
%	ARTICLE INFORMATION
%----------------------------------------------------------------------------------------    

\PaperTitle{Multi-characteristics reputation system \\ using iterative filtering} % Article title

\Authors{De Ron Malian, Laurent Quentin} % Authors

%----------------------------------------------------------------------------------------

\begin{document}

\flushbottom % Makes all text pages the same height

\maketitle % Print the title and abstract box

\thispagestyle{empty} % Removes page numbering from the first page

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section*{Introduction}
In this work we present a reputation system in which $N$ judges rate $M$ objects in $K$ characteristics. Previous methods are restricted to a single vote per judge/object where our method allows votes and reputations for several categories.
It also computes a weight for each judge. The applications of such system range from online video or e-shopping services and all kinds of databases. In some cases we expect that there will be some unreliable judges who are trying to favour a precise set of objects for their own purposes. In most cases, the reputation system used rely on the classic mean and hence assign equal influence to every judge, including the unreliable judges. In order to address this issue, we develop a method which will allow us to detect the partiality of a judge. 

\section*{Content}

\lettrine[lines=2]{O}{ur} aim is to be able to handle reputation systems where the judges rate on K aspects of an object, for instance the judges could rate some ice-skaters (objects) based on the technical and artistic aspects (K = 2 characteristics) of their performance in a competition. Before developing the model and the algorithm, we introduce the main notations in the following tabular.

\begin{table}[h]
\centering
\begin{tabular}{@{}ccl@{}}
\toprule
Tensor & Size                  & Definition                                                                                                     \\ \midrule
$X$    & $N \times M \times K$ & $X_{ijk}$ is the evaluation given by rater i\\
          &                                     &  to object j on characteristic k. \\
$A$    & $N \times M \times K$ & The adjacency matrix. $A_{ijk} = 1$ if \\
          &                                & rater $i$ evaluates $j$ on characteristic $k$, \\
          &                                & otherwise $A_{ijk} = 0$. \\
$R$    & $M \times K$          & The reputation matrix of objects. \\
$w$    & $N \times 1$          & The weight vector.     \\
$m_i$ & $N \times 1$          & Sum of characteristics evaluated by i. \\                                                                                      
\end{tabular}
\end{table}

An iterative filtering (IF) system is composed of two basic functions \cite{Cristo1}: The reputation function $F(w, X) = r$ that gives the reputation matrix from the weights and ratings, and the filtering function $G(r, X) = w$ that gives the weight from the reputations and ratings. We have choosen a filtering function that ensures convergence and the reputation function is given by the weighted average of the votes, which gives us the following iteration
\[
    R^{t+1}_{jk} = \frac{\sum_i X_{ijk}w_i}{\sum_i A_{ijk} w_i}
    \qquad
    w^{t+1}_i = 1 - k \cdot \mathrm{div}^t_i
\]
where we defined a measure of \textbf{belief divergence} $\mathrm{div}_i$ in order to determine the weights of the judges. But before we introduce a vector $d^{ij}_k = X_{ijk} - A_{ijk} \cdot r_{jk}$, that can be seen as the distance of the ratings of the judge $i$ for object $j$ from the reputation of the object $j$. Then an easy measure of belief divergence would be
\[
   \mathrm{div}_i = \frac{1}{m_i} \sum_{j=1}^{N} (d^{ij})^T(d^{ij})
\]

This iteration scheme should give a judge that has higher belief divergence a lower weight.\\

We demonstrate certain properties of this method. For example, the fixed points of the system are the stationary points of the following energy function with $g(u) = 1 - k u$
\[
    E(r) = \sum_{i=1}^{n}\int_0^{\mathrm{div}_i} g(u) \mathrm{d}u + c
\]

Moreover, one iteration in the system corresponds to a steepest descent step $r^{t+1} = r^t - \alpha_t \nabla_r E(r^t)$ with $\alpha^t = \frac{MK}{2\sum_{i=1}^N w_i^t}$. From it we can say that the method will actually find the reputation that will maximize the $\| \cdot \|_2$ of the weight vector. So it will favour a few large weights over more average weights. In other words, we maximize some kind of confidence but we want to be able to know which judges are to be trusted more. This energy function will prove useful when looking for convergence and uniqueness results. Indeed, we also have proved the uniqueness of the stationary point and convergence of the iterative method under the condition that $k$ is such that all weights are positive.

We have also showed that the iterative method does not allow the potential cheater to know what to do in advance to favour some objects because the final reputation will not evolve monotonously according to a certain rating. We determined that when one judge modifies his ratings from $X_{tjk}$ to $X'_{tjk}$, the new reputations are on one side of the following hyperplane : 
\[ \langle c, r'^{\star} - r^{\star} \rangle \geq 0 \quad \text{ with } c_{jk} = ( w'_t(r^{\star})- w_t) (X'_{tjk}-r^{\star}_{jk}) + w_t(X'_{tjk}-X_{tjk}) \]
where $r^{\star}$ are the old reputation, $w_t = G_t(r^{\star},X)$ and $w'_t = G_t(r^{\star},X')$ and $r'^{\star}$ the new reputation. 
\\

Although the method is good at detecting and eliminating the cheaters, this effect can be subdued by the introduction of a cheater with very high belief divergence, who will limit the maximum value of $k$ and hide other cheaters.

We finally validated our method on two examples : the applied mathematics scores and the TripAdvisor database. We validated the robustness against cheaters.

\section*{Conclusion}
The use of iterative filtering is a fair approach in cases where we do not entirely trust they votes received as input. Instead of simply averaging them or suppressing the outliers, every one of them is taken in account according to the trust we grant the corresponding judge. The cheaters who are completely inconsistent with the other ratings are easily detected by our methods. Convergence and uniqueness results are proved. The influence of $k$ over the final results is characterized, and we see that the limitation on $k$ can be a shortcoming of the method.
As we extended the mono-characteristic case to the multi-characteristic one, this approach can be further extended to more dimensions if need be. We could think of the point of view of a judge as a new dimension for the votes.

\phantomsection
\bibliographystyle{unsrt}
\begin{thebibliography}{9}
   \bibitem{Cristo1}
          Cristobald de Kerchove and Paul Van Dooren
          Iterative Filtering for a Dynamical Reputation System.
          CoRR,
          abs/0711.3964,
          2007.
\end{thebibliography}


\end{document}