\documentclass[12pt,a4paper,notitlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\title{Description of the project : Reputation of objects and reliability of judges}
\author{Malian De Ron \and Quentin Laurent}
\begin{document}

\maketitle

\subsection*{Context}
In order to illustrate the applications of a reputation system, we take the example of several judges rating participants on the quality of a performance. The partiality of a judge can be detected, and the iterative method developped in \cite{Cristo1} seems to eliminate that kind of behavior by giving judges with high standard deviation in their rating a smaller weight in the final score computation.

However this method simply works when one aspect of the performance is rated, i.e. for $N$ judges and $M$ objects. Our aim is to be able to handle reputation systems where the judges rate on $K$ aspects of a performance, for instance the technical and artistic aspects. 
Going even further, the judges could rate the characteristics according to their own mood or point of view. For example, when rating an hotel, someone might think of the swimming pool, service, rooms, .. (characteristics) differently if he comes with his family or his mate (point of view).

\subsection*{Project stages}
We intend to follow three distinct steps in order to make our project gradually evolve. At each step we will validate our theoretical results and our algorithms with tests on real or synthetic data.

\subsubsection*{Comparison between filtering methods}
At first, we will simply compare the iterative filtering presented in \cite{Cristo1} 
 with, e.g. the outlier method. The outlier method consists of suppressing the lowest and highest ratings for each object.\\
 This starter should allow us to get acquainted with the filtering methods.

\subsubsection*{Multi-variate version of the reputation system : $M$ objects, $K$ characteristics}
Objects will be rated on several aspects, building a more complex object profile. The vector of characteristics of the object can be sparse or full.
This part will deal with objects being rated on different characteristics. 
Here we define several guidelines for the choice of our filtering algorithm. It should be able to handle several cases :
\begin{itemize}
\item A judge rating one object much better than the others in a caracteristic should be given less influence
\item A judge rating with a mean rating above or below the average of the other judges should have his points adjusted or his influence in the final rating diminished.
\item The variance of the ratings for a given judge and characteristic should also be included in the equation
\end{itemize}

\subsubsection*{Adding a dimension : $M$ objects, $K$ characteristics and $L$ points of view}
The judges will give ratings according to several points of view. The problem is the same, but its size will be increased and the notations will have to be adjusted to include the additional dimension.
\subsection*{Underlying objectives}
There are several intermediary objectives that we will try and fulfill for each of the project stages outlined above.
\begin{itemize}
\item We need to establish mathematically the convergence of our iteration scheme and eventually find ways to improve it.
\item Analyze a range of behaviours for spammers and cheaters to check the robustness of our method. Tests on several data sets
\item Interpret our method statistically
\end{itemize}


\newpage
\section{Appendix 1 : Model and notations}
\input{tex/model.tex}

\bibliographystyle{plain}
\bibliography{bib/biblio}
\nocite{*}


\end{document}